Improved Particle Approximations \\ to the Joint Smoothing Distribution \\ Using Markov Chain Monte Carlo

### 2012-06-08 Paper/complete/response_to_reviewers.tex

\documentclass{article}

\usepackage{amsmath}
\usepackage{IEEEtrantools}
\usepackage{color}

\newenvironment{meta}[0]{\color{red} \em}{}

\begin{document}

{\meta Since submitting this paper, we've discovered a related piece of work, ``Particle approximation improvement of the
joint smoothing distribution with on-the-fly variance estimation'' by Dubarry and Douc. This is available as an arXiv preprint (arXiv:1107.5524) http://arxiv.org/abs/1107.5524 . The algorithm it contains shares some characteristics with our backwards proposing smoother. We've added a reference in section IV, along with a brief comparison.  }

Reviewer Comments:

Reviewer: 1

Recommendation: AQ - Publish In Minor, Required Changes

Comments:
An improved particle filtering approach using MCMC is proposed in this paper. The work is novel and the paper is pleasant to read. Some minor points are listed here for consideration.

1) Make sure that paragraphs are properly used. Quite a lot of paragraphs can be merged, e.g., line 42 on page 2.
{\meta I've merged a few, but I like to have a separate paragraph for each point I make. I consider this a matter of taste. }

2) Check all punctuation symbols.
{\meta Done. Yes. Whoops.}

3) Algorithm initialization is not clear in simulations.
{\meta Added a sentence about this.}

4) Reorganize section IV, if necessary.
{\meta I think it is fine.}

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Yes

2. Is the topic important to colleagues working in the field?: Yes

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Yes

3. How would you describe technical depth of paper?: Appropriate for the Generally Knowledgeable Individual Working in the Field or a Related Field

4. How would you rate the technical novelty of the paper?: Novel

1. How would you rate the overall organization of the paper?: Could be improved

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the length of the paper should be amended, including a possible target length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Needs improvement

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Sufficiently Novel

3. How would you rate the "literary" presentation of the paper?: Totally Accessible

4. How would you rate the appropriateness of this paper for publication in this IEEE Transactions?: Excellent Match

Reviewer: 2

Recommendation: RQ - Review Again After Major Changes

Comments:
This has the makings of a really nice paper. However, I am bothered by a few things and I think addressing these could transform the paper from being slightly interesiting (as it is) to really great (as it could be).

1) I'm bothered that the authors seem to have a very different view of [13] to me. Certainly, the comments about [13] are probably based on the authors' experience, in which case the text should be softened a little to say so. It would be even better if the techniques in [13] were included in the analysis: the point of [13] (as I understand it) was to change the scaling of the computational complexity, which is clearly a key part of the approach described in the current submission. Exlcuding such a comparison only devalues the submission.

{\meta An interesting point. Our glib dismissal of the this reference is definitely inappropriate given the subject matter, and the reasoning was wrong. However, if I understand correctly, the methods in this paper revolve around fast approximation of summation of function values over a particle population. They are, therefore, tailored towards algorithms for marginal smoothing. For the joint smoothing task considered in our paper, we need to sample from these particle populations, and this is the basis on which we do not consider these fast approximations further. The text has been modified to this effect. }

2) The RMSE results are not very convincing: the differences are small. Indeed, the results could be more convincing: specifically, using NEES (alongside RMSE) would be a good way to downplay the small differences in RMSE and upplay the differences in the number of unique particles in terms of a performance metric that "matters".

{\meta Yes. Very true. A proper NEES score would require us to know the true posterior means and covariances. Since we can't calculate these for a nonlinear model, I've used an empirical form - details in the paper. }

3) The values used in the two cases for the bearing and range accuracy aren't actually that different in their nature. Indeed the cases differ in terms of the absolute value of the noise, but not (much) in its correlation structure. Changing the absolute value of the noise alters the implicit time constant associated with the posterior. I accept that this is interesting since it stresses the ability of the smoother to explore the space. However, the interesting bit about the bearing and range likelihood is when the likleihood function becomes heavily skewed (ie "banana" shaped). Adding a case with a different degree of skewness (eg using $\sigma_B^2 = (\pi/36)^2$ and $\sigma_R^2 = 0.1$) would be really interesting and would strengthen the paper.

{\meta Ok. Done. }

I also spotted a few bits of niff-naff-and-trivia that the authors could sensibly (and easily) address:
1) "using the a Rauch-Tung-Striebel (RTS) smoother" -> "using the Rauch-Tung-Striebel (RTS) smoother" (typo)
2) The first line of (7) is slightly non-standard and results in the approximation in the final line. It would be better if a full path was considered such that equalities alone were used.

{\meta The approximation is a typo. It was actually intentional not to use the full path, to emphasise the difference between the filter and the filter-smoother. By marginalising $x_{n-1}$ after each step, we get the same filter output as if we used the full path. }

3)  "backwards-resampling" is a really misleading name given the use of "resampling" in the (forwards) particle filter. Why not call it "backwards-resimulation"? I realise that this would be a new term, but it might be helpful to distinguish "resampling" and "resampling"!!

{\meta Yes. I was worried about this myself. I've renamed all the algorithms. }

Additional Questions:
1. Is the topic appropriate for publication in these transactions?: Yes

2. Is the topic important to colleagues working in the field?: Yes

Explain:

1. Is the paper technically sound?: Yes

why not?:

2. Is the coverage of the topic sufficiently comprehensive and balanced?: Important Information is missing or superficially treated.

3. How would you describe technical depth of paper?: Appropriate for the Generally Knowledgeable Individual Working in the Field or a Related Field

4. How would you rate the technical novelty of the paper?: Novel

1. How would you rate the overall organization of the paper?: Satisfactory

2. Are the title and abstract satisfactory?: Yes

Explain:

3. Is the length of the paper appropriate? If not, recommend how the length of the paper should be amended, including a possible target length for the final manuscript.: Yes

4. Are symbols, terms, and concepts adequately defined?: Yes

5. How do you rate the English usage? : Satisfactory

6. Rate the Bibliography: Satisfactory

null:

1. How would you rate the technical contents of the paper?: Good

2. How would you rate the novelty of the paper?: Sufficiently Novel

3. How would you rate the "literary" presentation of the paper?: Totally Accessible

4. How would you rate the appropriateness of this paper for publication in this IEEE Transactions?: Excellent Match

\end{document}

### 2012-06-08 Paper/complete/revisions_single_MCMCsmoother.tex
submitted revisions

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\begin{IEEEkeywords}
state space model, particle filter, smoothing, MCMC, Bayesian inference
\end{IEEEkeywords}

@@

The proposal for $x_k$, $q(x_{x}|x_{k-1})$, is often called the ``importance density''. Common choices for this include the model transition density (\ref{eq:state_proc}), and the ``optimal importance density'' \cite{Doucet2000a}. The proposal density for $x_{k-1}$, $q(x_{k-1})$, is constructed from the particles of the filtering approximation from the previous time step. The choice of weights and sampling procedure for $x_{k-1}$ determines what from of ``resampling'' is to be used. Here we use arbitrary weights for generality,
%
\begin{IEEEeqnarray}{rCl}
q(x_{k-1}) & = & \sum_i v_{k-1}^{(i)} \delta_{x_{k-1}^{(i)}}(x_{k-1})     .
\end{IEEEeqnarray}

The choice $v_{k-1}^{(i)} = w_{k-1}^{(i)}$ corresponds to ordinary resampling, and other choices of $v_{k-1}^{(i)}$ represent auxiliary sampling schemes \cite{Pitt1999,Cappe2007}. For the least computational expense, the proposal density with weights $v_{k-1}^{(i)} = 1/N_F$ (where $N_F$ is the number of filter particles) can be ``sampled'' by simply keeping the set of particles generated in the last step, with no resampling. This, however, leads to degeneracy of the particle weights over time. (See \cite{Douc2005,Cappe2007,Doucet2009} for further discussion of resampling.)

@@

Following an equivalent derivation to that for (\ref{eq:backward_conditional_filter}), the target distribution may be approximated by a particle distribution,
%
\begin{IEEEeqnarray}{rCl}
\hat{p}(x_{1:k}|\tilde{x}_{k+1}, y_{1:K}) = \sum_i  \tilde{w}_k^{(i)} \delta_{x_{1:k}^{(i)}}(x_{1:k}) \\
\tilde{w}_k^{(i)} \propto w_k^{(i)} p(\tilde{x}_{k+1}|x_k^{(i)}) \label{eq:MCMC-BRS_weights}   .
\end{IEEEeqnarray}

@@

This new scheme bears a resemblance to the ``linear cost'' simulation scheme of \cite{Douc2009} which uses rejection sampling instead of MH. Although theoretically elegant, the latter algorithm has been found to suffer from such high rejection rates as to render it consistently slower than the direct sampling implementation on problems with more than 1 state dimension (see section~\ref{sec:simulations}).

@@

10 realisations of 500 time steps were simulated from the model and the algorithms tested on each one. Results are shown here for high and low observation noise cases. For case 1, the observation variances were set to $\sigma_B^2 = (\pi/720)^2$ and $\sigma_R^2 = 0.1$. For case 2, $\sigma_B = (\pi/36)^2$ and $\sigma_R^2 = 100$. Other model settings are $\Delta t = 1$, $\sigma_P = 1$, and $x_0 = [-100, 50, 10, 0]^T$. Example trajectories and observations from the two cases are shown in Fig.~\ref{fig:example_trajectories}.

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.9\columnwidth]{case1_trajectory.pdf}%
\label{fig_first_case}}
\\
\subfloat[Case 2]{\includegraphics[width=0.9\columnwidth]{case2_trajectory.pdf}%
\label{fig_second_case}}
\caption{Example trajectory with observations from the two noise covariance cases.}
\label{fig:example_trajectories}
\end{figure}

@@

\noindent and where $\mathbf{x}_k^*$ is the true value of the state. This statistic has a value of $1$ when there fewer linearly independent state values in the particle approximation than state dimensions, and tends to $0$ as the number of independent particles tends to infinity. It provides a relative measure of the quality of different particle approximations, taking into account both estimation error and particle diversity. Finally, the mean number of unique particles at each time instant and the running times (excluding the time for filtering) are also recorded. These performance indicators are all shown in tables~\ref{tab:case1_performance} and~\ref{tab:case2_performance} for the two noise scenarios. The trade-off between speed and error is shown in Fig.~\ref{fig:rmse_vs_time}.

%Tables~\ref{tab:case1_performance} and~\ref{tab:case2_performance} show the root-mean-square errors (RMSEs) in position and velocity obtained by the different algorithms in the two noise scenarios, along with running times (excluding the time for filtering) and the mean number of unique smoother particles at each time instant. The trade-off between speed and error is shown in Fig.~\ref{fig:rmse_vs_time}.

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 1. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
{\scriptsize
\centering
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS              & 0.578 & 0.968 &  & 0 & 2.25 \\
D-FFBS          & 0.475 & 0.762 &  & 122 & 20.3 \\
\hline
MH-FFBS (1)    & 0.509 & 0.823 &  & 3 & 13.7  \\
MH-FFBS (3)    & 0.493 & 0.790 &  & 7 & 17.4  \\
MH-FFBS (10)   & 0.482 & 0.768 &  & 21 & 19.6 \\
MH-FFBS (30)   & 0.480 & 0.761 &  & 62 & 20.2 \\
MH-FFBS (100)  & 0.476 & 0.764 &  & 202 & 20.4  \\
\hline
MH-FFBP (1)    & 0.473 & 0.758 &  & 14 & 44.3 \\
MH-FFBP (3)    & 0.461 & 0.734 &  & 29 & 69.7 \\
MH-FFBP (10)   & 0.451 & 0.720 &  & 82 & 89.8 \\
MH-FFBP (30)   & 0.444 & 0.713 &  & 232 & 96.7 \\
MH-FFBP (100)  & 0.443 & 0.709 &  & 755 & 98.6 \\
\hline
\end{tabular}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 2. All results are averaged over 10 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
{\scriptsize
\centering
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS              & 6.17 & 2.03 &  & 0 & 3.96 \\
D-FFBS         & 5.79 & 1.89 &  & 63 & 7.34 \\
\hline
MH-FFBS (1)    & 6.13 & 2.01 &  & 2 & 4.77 \\
MH-FFBS (3)    & 6.07 & 1.99 &  & 4 & 5.29 \\
MH-FFBS (10)   & 5.94 & 1.94 &  & 10 & 6.1 \\
MH-FFBS (30)   & 5.82 & 1.91 &  & 29 & 6.73 \\
MH-FFBS (100)  & 5.80 & 1.89 &  & 95 & 7.38 \\
\hline
MH-FFBP (1)    & 5.90 & 1.91 &  & 9 & 12.6 \\
MH-FFBP (3)    & 5.67 & 1.81 &  & 18 & 22.7 \\
MH-FFBP (10)   & 5.48 & 1.73 &  & 50 & 44.1 \\
MH-FFBP (30)   & 5.43 & 1.69 &  & 144 & 70.9 \\
MH-FFBP (100)  & 5.34 & 1.68 &  & 471 & 91.8 \\
\hline
\end{tabular}
}
\end{table}

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.9\columnwidth]{case1_smoother_comparison_posRMSE_time.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.9\columnwidth]{case2_smoother_comparison_posRMSE_time.pdf}}
\caption{Position RMSEs and running times of various smoothing algorithms with different noise covariance cases.}%
\label{fig:rmse_vs_time}%
\end{figure}

{\meta Add comments on ENEES.}

@@

When the number of MH steps, $M$, is small, the error of the MH-FFBS is only very slightly larger than that of the D-FFBS but with a significantly shorter running time. For a particular application, it is possible to adjust $M$ to control the trade-off between error and speed of computation. Thus, the MH-FFBS provides increased flexibility when compared to the D-FFBS scheme.

The MH-FFBP outperforms all of the other smoothers, achieving the lowest RMSE for any given running time. Furthermore, because the support is not limited to using states from the filter distributions, the smoothing particle approximation has many more unique particles, giving a less degenerate representation.

@@

\bibliographystyle{IEEEtran}
\bibliography{D:/pb404/Dropbox/PhD/Cleanbib}

>>>>

% correct bad hyphenation here
\hyphenation{}

@@

%\begin{IEEEkeywords}
%state space model, particle filter, smoothing, MCMC, Bayesian inference
%\end{IEEEkeywords}

\ifCLASSOPTIONpeerreview
\begin{center} \bfseries EDICS Categories: MLR-BAYL, SSP-NGAU, SSP-TRAC, SSP-FILT \end{center}
\fi

\newpage
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
%\IEEEpeerreviewmaketitle

@@

The proposal for $x_k$, $q(x_{x}|x_{k-1})$, is often called the ``importance density''. Common choices for this include the model transition density (\ref{eq:state_proc}), and the ``optimal importance density'' \cite{Doucet2000a}. The proposal density for $x_{k-1}$, $q(x_{k-1})$, is constructed from the particles of the filtering approximation from the previous time step. The choice of weights and sampling procedure for $x_{k-1}$ determine what form of ``resampling'' is to be used. Here we use arbitrary weights for generality,
%
\begin{IEEEeqnarray}{rCl}
q(x_{k-1}) & = & \sum_i v_{k-1}^{(i)} \delta_{x_{k-1}^{(i)}}(x_{k-1})     .
\end{IEEEeqnarray}

The choice $v_{k-1}^{(i)} = w_{k-1}^{(i)}$ corresponds to ordinary resampling, and other choices of $v_{k-1}^{(i)}$ represent auxiliary sampling schemes \cite{Pitt1999,Cappe2007}. For the least computational expense, the proposal density with weights $v_{k-1}^{(i)} = 1/N_F$ (where $N_F$ is the number of filter particles) can be ``sampled'' by simply keeping the set of particles generated in the last step, with no resampling. This, however, leads to degeneracy of the particle weights over time. (See \cite{Cappe2007,Doucet2009} for further discussion of resampling.)

@@

Following an equivalent derivation to that for (\ref{eq:backward_conditional_filter}), the target distribution may be approximated by a set of particles,
%
\begin{IEEEeqnarray}{rCl}
\hat{p}(x_{1:k}|\tilde{x}_{k+1}, y_{1:K}) = \sum_i  \tilde{w}_k^{(i)} \delta_{x_{1:k}^{(i)}}(x_{1:k}) \\
\tilde{w}_k^{(i)} \propto w_k^{(i)} p(\tilde{x}_{k+1}|x_k^{(i)}) \label{eq:MCMC-BRS_weights}   .
\end{IEEEeqnarray}

@@

This new scheme bears a resemblance to the ``linear cost'' simulation scheme of \cite{Douc2009} which uses rejection sampling instead of MH. Although theoretically elegant, the latter algorithm has been found to suffer from such high rejection rates as to render it consistently slower than the direct sampling implementation on problems with more than one state dimension (see section~\ref{sec:simulations}).

@@

100 realisations of 500 time steps were simulated from the model and the algorithms tested on each one. Results are shown here for three noise parameter sets. For case 1, the observation variances were set to $\sigma_B^2 = (\pi/720)^2$ and $\sigma_R^2 = 0.1$. For case 2, $\sigma_B^2 = (\pi/36)^2$ and $\sigma_R^2 = 0.1$, resulting in a highly skewed likelihood function. For case 3, $\sigma_B = (\pi/36)^2$ and $\sigma_R^2 = 100$. Other model settings are $\Delta t = 1$, $\sigma_P = 1$, and $x_0 = [-100, 50, 10, 0]^T$. Example trajectories and observations from the two cases are shown in Fig.~\ref{fig:example_trajectories}.

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_trajectory.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_trajectory.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.45\columnwidth]{case3_trajectory.pdf}}
\caption{Example trajectory with observations from the two noise covariance cases. Constant likelihood contours are shown for the first and last position (dashed)}
\label{fig:example_trajectories}
\end{figure}

@@

\noindent and where $\mathbf{x}_k^*$ is the true value of the state. This statistic has a value of $1$ when there are fewer linearly independent state values in the particle approximation than state dimensions. It decreases as the number of independent particles increases (improving the covariance estimate) or the estimation error decreases. Thus, it provides a simple relative measure of the quality of different particle approximations, taking into account both estimation error and particle diversity. Finally, the mean number of unique particles at each time instant and the running times (excluding the time for filtering) are also recorded. These performance indicators are all shown in tables~\ref{tab:case1_performance}--\ref{tab:case3_performance} for the two noise scenarios. The trade-off between speed and error is shown in Fig.~\ref{fig:rmse_vs_time}.

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 1. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 0.56 & 0.96 & 0.99 & 0.00 & 2.13 \\
D-FFBS         & 0.45 & 0.76 & 0.84 & 65.88 & 20.54 \\
\hline
MH-FFBS (1)    & 0.48 & 0.81 & 0.90 & 1.80 & 13.95 \\
MH-FFBS (3)    & 0.46 & 0.78 & 0.87 & 3.89 & 17.63 \\
MH-FFBS (10)   & 0.46 & 0.77 & 0.85 & 11.20 & 19.83 \\
MH-FFBS (30)   & 0.45 & 0.76 & 0.84 & 32.05 & 20.40 \\
MH-FFBS (100)  & 0.45 & 0.76 & 0.84 & 105.12 & 20.55 \\
\hline
MH-FFBP (1)    & 0.45 & 0.75 & 0.82 & 9.20 & 44.32 \\
MH-FFBP (3)    & 0.43 & 0.73 & 0.79 & 19.23 & 70.12 \\
MH-FFBP (10)   & 0.43 & 0.72 & 0.78 & 54.33 & 90.10 \\
MH-FFBP (30)   & 0.42 & 0.71 & 0.79 & 154.47 & 96.89 \\
MH-FFBP (100)  & 0.42 & 0.70 & 0.79 & 504.58 & 98.53 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 2. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 8.01 & 1.90 & 0.99 & 0.00 & 2.75 \\
D-FFBS         & 7.71 & 1.70 & 0.92 & 66.40 & 14.06 \\
\hline
MH-FFBS (1)    & 7.91 & 1.83 & 0.98 & 1.79 & 6.51 \\
MH-FFBS (3)    & 7.83 & 1.78 & 0.96 & 3.86 & 8.63 \\
MH-FFBS (10)   & 7.77 & 1.73 & 0.93 & 11.09 & 11.39 \\
MH-FFBS (30)   & 7.75 & 1.71 & 0.92 & 31.77 & 13.14 \\
MH-FFBS (100)  & 7.70 & 1.70 & 0.92 & 104.14 & 13.88 \\
\hline
MH-FFBP (1)    & 7.75 & 1.72 & 0.92 & 9.25 & 22.97 \\
MH-FFBP (3)    & 7.67 & 1.67 & 0.88 & 19.34 & 42.22 \\
MH-FFBP (10)   & 7.62 & 1.63 & 0.85 & 54.61 & 70.06 \\
MH-FFBP (30)   & 7.60 & 1.61 & 0.84 & 155.38 & 88.81 \\
MH-FFBP (100)  & 7.59 & 1.60 & 0.84 & 507.58 & 96.82 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 3. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case3_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS            & 7.41 & 2.15 & 0.98 & 0.00 & 3.97 \\
D-FFBS        & 7.19 & 2.03 & 0.97 & 66.27 & 7.48 \\
\hline
MH-FFBS (1)   & 7.39 & 2.14 & 0.98 & 1.75 & 4.79 \\
MH-FFBS (3)   & 7.36 & 2.12 & 0.98 & 3.75 & 5.33 \\
MH-FFBS (10)  & 7.30 & 2.08 & 0.98 & 10.78 & 6.16 \\
MH-FFBS (30)  & 7.24 & 2.05 & 0.97 & 30.83 & 6.88 \\
MH-FFBS (100) & 7.20 & 2.04 & 0.97 & 101.02 & 7.38 \\
\hline
MH-FFBP (1)   & 7.22 & 2.05 & 0.97 & 9.12 & 12.57 \\
MH-FFBP (3)   & 7.08 & 1.98 & 0.94 & 19.01 & 22.78 \\
MH-FFBP (10)  & 6.95 & 1.92 & 0.92 & 53.64 & 44.15 \\
MH-FFBP (30)  & 6.87 & 1.88 & 0.90 & 152.42 & 70.71 \\
MH-FFBP (100) & 6.84 & 1.86 & 0.88 & 498.38 & 91.35 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_smoother_comparison_posRMSE_time.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_smoother_comparison_posRMSE_time.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.45\columnwidth]{case3_smoother_comparison_posRMSE_time.pdf}}
\caption{Position RMSEs and running times of various smoothing algorithms with different noise covariance cases.}%
\label{fig:rmse_vs_time}%
\end{figure}

@@

When the number of MH steps, $M$, is small, the error of the MH-FFBS is often still significantly reduced relative to the D-FFBS but with a shorter running time. For a particular application, it is possible to adjust $M$ to control the trade-off between error and speed of computation. Thus, the MH-FFBS provides increased flexibility when compared to the D-FFBS scheme.

The MH-FFBP outperforms all of the other smoothers, achieving the lowest RMSE and ENEES for any given running time. Furthermore, because the support is not limited to using states from the filter distributions, the smoothing particle approximation has many more unique particles, giving a less degenerate representation.

@@

\newpage
\bibliographystyle{IEEEtran}
\bibliography{D:/pb404/Dropbox/PhD/Cleanbib}
